%\chapter*{{Bibliographie}}\addcontentsline{toc}{chapter}{{Bibliographie}}


\begin{thebibliography}{KNU90}\addcontentsline{toc}{chapter}{{Bibliographie}}
\bibitem{Krotov1} Krotov, V.F., Feldman, I.N.
\emph{Iterative methods for solving extreme problems}. In the
book: Modeling of technical and economic processes, Moscow, Moscow Economic and Statistical Institute (MESI) Publ. (1978), 54–65. (en russe)
\vspace{0.5cm}
\bibitem{Krotov2} Krotov, V.F., Feldman, I.N.
\emph{An iterative method for solving problems of optimal control}. Engineering Cybernetics, 21:2 (1983), 123–130.
\vspace{0.5cm}
\bibitem{Tannor} Tannor, D., Kazakov, V., Orlov, V.
\emph{Control of photochemical branching: Novel procedures for finding optimal pulses and global upper bounds}. Time Dependent Quantum Molecular Dynamics, edited by Broeckhove J. and Lathouwers L. Plenum, 347–360 (1992)
\vspace{0.5cm}
\bibitem{Zhu} Zhu, W., Rabitz, H.
\emph{A rapid monotonically convergent iteration algorithm for quantum optimal control over the expectation value of a positive definite operator}. J. Chem. Phys. 109, 385–391 (1998)
\vspace{0.5cm}
\bibitem{Maday} Maday, Y., Turinici, G. 
\emph{New formulations of monotonically convergent quantum control algorithms}. J. Chem. Phys. 118, 8191–8196 (2003)
\vspace{0.5cm}
\bibitem{Salomon} Maday, Y., Salomon, J. and Turinici, G..
\emph{Monotonic time-discretized schemes in quantum control}. Num. Math., 2005.
\vspace{0.5cm}
\bibitem{These} Salomon, J.
\emph{Contrôle en chimie quantique : conception et analyse de schémas d’optimisation}. 2005.
\vspace{0.5cm}
\bibitem{Strang} Strang, G. 
\emph{Accurate partial difference methods I: Linear Cauchy problems.}. Arch. Rat. Mech. and An. 12, 392–402 (1963)
\vspace{0.5cm}
\bibitem{Trelat} Trélat, E.
\emph{Contrôle optimal : théorie et applications}. avril 2016.
\vspace{0.5cm}
\bibitem{Fattorini} Fattorini, H.O., Kerber, A.
\emph{The Cauchy problem} Encyclopedia of mathematics and its applications 18. Section, Analysis. -Cambridge Press. 2009.
\vspace{0.5cm}
\bibitem{Dossa} Dossa, A.
\emph{Cours de Physique Quantique}. 2015-2016.
\vspace{0.5cm}
\bibitem{Glorieux} Glorieux, Q.
\emph{Cours 4 – Les principes de la mécanique quantique
3P001 – Universite Pierre et Marie Curie}. 2015-2016.
\vspace{0.5cm}
\bibitem{Dong} Dong, D., Petersen, I.R.
\emph{Quantum control theory and applications: A survey}. 2011.
\vspace{0.5cm}
\bibitem{Bidegaray} Bidégaray-Fesquet, B.
\emph{Méthodes numériques avancées pour la finance. — Méthodes de splitting}. 2009-2010.
\vspace{0.5cm}
\bibitem{Cances} Cancès, E., Le Bris, C., Pilot., M.
\emph{Optimal bilinear control for a Schrödinger equation}. C. R. Acad. Sci. Paris, 330 (Série 1) : 567–571, 2000.
\vspace{0.5cm}
\bibitem{Baudouin} Baudouin, L., Puel., J-P.
\emph{Bilinear optimal control problem on a Schrödinger equation with singular potentials}. 2005.
\vspace{0.5cm}
\bibitem{Baudouin} Eaton, J.W., et al.
\emph{GNU Octave version 3.8.1 manual: a high-level interactive language for numerical computations}. CreateSpace Independent Publishing Platform. 2014.
\end{thebibliography}
